Paper_Results

### 2025-06-10 Paper_Results.Rmd
revisions

## Pitfall 1: Within person performance Emprircal Example
```{r }
### Descriptives

# Read the CSV files
final_results_df_2_b <- read.csv("final_results_df_2_b.csv")
final_results_df_3_b <- read.csv("final_results_df_3_b.csv")
final_results_df_4_b <- read.csv("final_results_df_4_b.csv")
final_results_df_5_b <- read.csv("final_results_df_5_b.csv")

# Select specific columns
cols_to_select1 <- c("outcome", "overall_prob_outcome", "sd_outcome",
                  "icc_data")
cols_to_select <- c("overall_prob_outcome", "sd_outcome",
                   "icc_data")

df2_selected <- final_results_df_2_b[, cols_to_select1]
df3_selected <- final_results_df_3_b[, cols_to_select]
df4_selected <- final_results_df_4_b[, cols_to_select]
df5_selected <- final_results_df_5_b[, cols_to_select]

# Rename columns to distinguish between dataframes (optional but recommended)
names(df2_selected) <- paste0(names(df2_selected), "_df2")
names(df3_selected) <- paste0(names(df3_selected), "_df3")
names(df4_selected) <- paste0(names(df4_selected), "_df4")
names(df5_selected) <- paste0(names(df5_selected), "_df5")

# Combine the selected dataframes column-wise
combined_df <- cbind(df2_selected, df3_selected, df4_selected, df5_selected)

# View or write the combined data frame
head(combined_df)

combined_df <- combined_df %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(combined_df, "combined_des_binary.csv", row.names = FALSE)

# Read the CSV files
final_results_df_2 <- read.csv("final_results_df_2.csv")
final_results_df_3 <- read.csv("final_results_df_3.csv")
final_results_df_4 <- read.csv("final_results_df_4.csv")
final_results_df_5 <- read.csv("final_results_df_5.csv")

# Select specific columns
cols_to_select1 <- c("outcome", "overall_prob_outcome", "sd_outcome",
                  "icc_data")
cols_to_select <- c("overall_prob_outcome", "sd_outcome",
                   "icc_data")

df2_selected <- final_results_df_2[, cols_to_select1]
df3_selected <- final_results_df_3[, cols_to_select]
df4_selected <- final_results_df_4[, cols_to_select]
df5_selected <- final_results_df_5[, cols_to_select]

# Rename columns to distinguish between dataframes (optional but recommended)
names(df2_selected) <- paste0(names(df2_selected), "_df2")
names(df3_selected) <- paste0(names(df3_selected), "_df3")
names(df4_selected) <- paste0(names(df4_selected), "_df4")
names(df5_selected) <- paste0(names(df5_selected), "_df5")

# Combine the selected dataframes column-wise
combined_df <- cbind(df2_selected, df3_selected, df4_selected, df5_selected)

# View or write the combined data frame
head(combined_df)

combined_df <- combined_df %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))
write.csv(combined_df, "combined_des_continious.csv", row.names = FALSE)

@@

data <- data %>%
  group_by(subject) %>%
  mutate(y = lag(wantedToFeel_goodAboutMe, n = 1))

@@

table <- rbind(r_1$overall_summary,r_3$overall_summary, r_4$overall_summary)
table$'AUC Overall' <- c(r_1$auc_value,r_3$auc_value,r_4$auc_value)
colnames(table) <-  c("Mean AUC within-person:", "SD AUC within-person:", "% of AUC > 0.5 within-person:", "N included within-person:", "AUC Overall")
rownames(table) <- c("row-wise","subject-wise","rolling-window")
table
```

@@

plot = ggplot(pred_true, aes(day, subject, color = factor(true), shape = prediction_correct)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_text(aes(label = ifelse(!duplicated(subject), paste("AUC: ", auc_val), "")),
            x = -Inf, hjust = 0, size = 3, color = "gray40") +  # AUC on the left side
  scale_color_manual(values = c("0" = "#FFB5A7", "1" = "#40916C")) +
  scale_shape_manual(values = c("Correct" = 15, "Incorrect" = 0)) +
  labs(color = NULL, shape = NULL) +  # Removes legend titles
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom",
    axis.text.y = element_blank(),
    axis.text.x = element_blank()     # Removes x-axis tick labels
  ) +
  xlim(-6, 75) +
  labs(y = paste0("Within-Person"), x = "") +
  ggtitle(paste("AUC evaluated over the whole dataset:", round(table$'AUC Overall', 2), "(Between-Person)")) +
  theme(text = element_text('Futura'),axis.title=element_text(size=14)) 
plot
ggsave("WithinBetween_Example.png", 
       width = 6100, height = 3000, units = "px", dpi = 800,plot = plot)

@@

>>>>

## Pitfall 1: Within person performance Emprircal Example

@@

data <- data %>%
  group_by(subject) %>%
  mutate(y = lag(wantedToFeel_goodAboutMe, n = 1)) # Lag outcome

@@

table <- rbind(r_1$overall_summary,r_3$overall_summary, r_4$overall_summary)
table$'AUC Overall' <- c(r_1$auc_value,r_3$auc_value,r_4$auc_value)
colnames(table) <-  c("Mean AUC within-person:", "SD AUC within-person:", "% of AUC > 0.5 within-person:", "N included within-person:", "AUC Overall")
rownames(table) <- c("row-wise","subject-wise","rolling-window")
round(table,2)
```

@@

@@

Other things that were not presented in the paper (but used for a presentation):

plot = ggplot(pred_true, aes(day, subject, color = factor(true), shape = prediction_correct)) + 
  geom_point(size = 2, alpha = 0.8) +
  geom_text(aes(label = ifelse(!duplicated(subject), paste("AUC: ", auc_val), "")),
            x = -Inf, hjust = 0, size = 3, color = "gray40") +  # AUC on the left side
  scale_color_manual(values = c("0" = "#FFB5A7", "1" = "#40916C")) +
  scale_shape_manual(values = c("Correct" = 15, "Incorrect" = 0)) +
  labs(color = NULL, shape = NULL) +  # Removes legend titles
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    legend.position = "bottom",
    axis.text.y = element_blank(),
    axis.text.x = element_blank()     # Removes x-axis tick labels
  ) +
  xlim(-6, 75) +
  labs(y = paste0("Within-Person"), x = "") +
  ggtitle(paste("AUC evaluated over the whole dataset:", round(table$'AUC Overall', 2), "(Between-Person)")) +
  theme(text = element_text('Futura'),axis.title=element_text(size=14)) 
plot
# ggsave("WithinBetween_Example.png", 
#        width = 6100, height = 3000, units = "px", dpi = 800,plot = plot)
